\documentclass[]{azhagu-swe-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LAST UPDATED DATE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     TITLE NAME
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Alaagappan}{P} { \urlstyle{same}
\href{mailto:azhagu.swe@gmail.com}{azhagu.swe@gmail.com} | \href{https://www.linkedin.com/in/azhagu-swe/}{LinkedIn.com/azhagu-swe } | +91 7502005724 | \href{https://azhagu-swe.github.io/portfolio/}{Portfolio}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN ONE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Languages}
Java | JavaScript | HTML | CSS | SQL  
\subsection{Frameworks}
Spring Boot| Next.js | React.js | MUI|\\
 Hibernate  |
 \subsection{Tools}
 Git | Postgresql | MySQL |
 \subsection{Platforms}
 windows | Ubuntu |
 
\sectionsep
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github: \href{https://github.com/azhagu-swe}{\bf  github.com/azhagu-swe } \\
Portfolio:  \href{https://azhagu-swe.github.io/portfolio/}{\bf azhagu-swe.github.io} \\
% LinkedIn://  \href{https://www.linkedin.com/in/azhagu-swe/}{\bf azhagu-swe} \\
% YouTube://  \href{https://www.youtube.com/user/azhagu-swe}{\bf azhagu-swe} \\
% Twitter://  \href{https://twitter.com/azhagu_swe}{\bf azhagu\_swe} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{H.H.The Rajah’s College}
\descript{M.Sc in Computer Science}
\location{Sep 2020 | Pudukottai, Tamil Nadu}
\location{ Percentage : 74 \%}
\sectionsep

\subsection{H.H.The Rajah’s College}
\descript{B.Sc in Computer Science}
\location{ April 2018 | Pudukottai, Tamil Nadu}
\location{ Percentage : 71 \%}
\sectionsep

\subsection{Valampuri Vaduganathan HR. SEC.School}
\location{ 2015|  Pudukottai, Tamil Nadu}
\location{ Percentage : 64 \%}
\sectionsep

\subsection{Govt. HR. SEC. School}
\location{ 2013|  Pudukottai, Tamil Nadu}
\location{ Percentage : 89 \%}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACHIEVEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Achievements}
 \textbf{Debugging Competition}: \\ Secured \textbf{Second Prize} in Debugging Competition, held at \textit{National College}, Trichy.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CERTIFICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Certifications}
\vspace{\topsep}
\begin{tightemize}
    \item \textbf{ Full Stack Java Development Course} \textit{SkillUP by Simplilearn}, \textcolor{gray}{2022}
    \item \textbf{Java Certification Course} \textit{SkillUP by Simplilearn}, \textcolor{gray}{2022}
\end{tightemize}
\sectionsep



\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COLUMN TWO
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Summary
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary}
Full-Stack Developer with 2+ years of experience in creating scalable software solutions using Java and Spring Boot.  
Proven ability to reduce latency (40% via Redis caching) and boost database performance (30% faster queries with PostgreSQL).  
Skilled in developing responsive, user-friendly interfaces with Next.js and React.js, delivering robust applications in high-traffic environments.
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{MEmob Plus Pvt Ltd}
\descript{| Junior Software Developer}
\location{Apr 2023 -- Present | Chennai, Tamil Nadu}
\vspace{\topsep}
\begin{tightemize}
    \item Modernized a legacy DSP by updating its \textbf{\textcolor{blue}{UI}} and \textbf{\textcolor{blue}{API}} for better performance.
    \item Developed scalable \textbf{\textcolor{blue}{RESTful APIs}} using \textbf{\textcolor{blue}{Java}} and \textbf{\textcolor{blue}{Spring Boot}} to lower latency.
    \item Built dynamic front-end components with \textbf{\textcolor{blue}{Next.js}} for interactive interfaces.
    \item Integrated \textbf{\textcolor{blue}{Redis}} caching and \textbf{\textcolor{blue}{RabbitMQ}} for efficient asynchronous processing.
    \item Reduced API latency by 40\% using targeted \textbf{\textcolor{blue}{Redis}} caching.
    \item Improved \textbf{\textcolor{blue}{PostgreSQL}} performance by 30\% via index tuning and query optimization.
    \item \textbf{Tech Stack}: \textbf{\textcolor{blue}{Java}}, \textbf{\textcolor{blue}{Spring Boot}}, \textbf{\textcolor{blue}{RabbitMQ}}, \textbf{\textcolor{blue}{Redis}}, \textbf{\textcolor{blue}{Next.js}}, \textbf{\textcolor{blue}{Redux}}, \textbf{\textcolor{blue}{MUI}}.
    \item \textbf{Database}: \textbf{\textcolor{blue}{PostgreSQL}}.
\end{tightemize}
\sectionsep

\runsubsection{MEmob Plus Pvt Ltd}
\descript{| Software Developer Intern}
\location{Aug 2022 -- Feb 2023 | Chennai, Tamil Nadu}
\begin{tightemize}
    \item Optimized database queries to speed up data retrieval.
    \item Implemented custom proximity hash in \textbf{\textcolor{blue}{Java}} for advanced geospatial targeting.
    \item Developed a proximity hash algorithm in \textbf{\textcolor{blue}{Java}}, boosting location targeting accuracy by 15\%.
    \item \textbf{Tech Stack}: \textbf{\textcolor{blue}{Java}}, \textbf{\textcolor{blue}{Spring Boot}}, \textbf{\textcolor{blue}{RabbitMQ}}, \textbf{\textcolor{blue}{Redis}}, \textbf{\textcolor{blue}{React.js}}, \textbf{\textcolor{blue}{Mapbox}}, \textbf{\textcolor{blue}{MUI}}.
    \item \textbf{Database}: \textbf{\textcolor{blue}{PostgreSQL}}.
\end{tightemize}
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}

\runsubsection{Portfolio}
\descript{Next.js Application}
\location{Sep 2024 | \textbf{\href{https://azhagu-swe.github.io/portfolio/}{Live Demo}} | \textbf{Git: \href{https://github.com/azhagu-swe/portfolio}{Portfolio}}}
\begin{tightemize}
\item Built a responsive portfolio with dynamic project filtering, increasing user engagement by 25\%.  
\item Achieved 95+ Lighthouse performance score using Next.js static site generation.  
\item Tech Stack: \textbf{Next.js}, \textbf{TypeScript}, \textbf{React.js}, \textbf{MUI}.  
\end{tightemize}
\sectionsep

\runsubsection{GeoHash Proximity Engine}
\descript{Java Geospatial Utility}
\location{May 2023 | \textbf{Git: \href{https://github.com/azhagu-swe/proximityhash-javas}{Proximityhash-javas}}}
\begin{tightemize}
    \item Converted Python's ProximityHash library to Java for geohash generation with 10-meter accuracy.
    \item Reduced geohash generation time by 20\% compared to the Python version.
    \item Deployed in a production DSP to target over 1M mobile devices via geohash lookups.
    \item \textbf{Tech Stack}: \textbf{Java}, \textbf{Geohash Algorithm}, \textbf{GeoRaptor Compression}.
\end{tightemize}
\sectionsep

\end{minipage} 
\end{document} 
